Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-07 sections/01-introduction.tex
Update on Overleaf.

The paper is structured as follows. In section \ref{sec:trending} we formalize the concept of trending independently of the application domain and investigate quantification approaches for noise-free and noisy data. In particular, we introduce a new graphical method for evaluating trending, the conditional trending plot, which can represent the simultaneous evaluation of different intervals and asymmetries. Bootstrap methods for calculating confidence intervals for trending measures are also presented. In Section \ref{sec:application}, we show the results of applying our method to several practical examples from measurement, forecasting and nowcasting. We conclude our paper with the last section. The source code for the replication of the results of our study as well as a ready-to-use code for trendability detection are available in our public repository at ... available.

>>>>

The paper is structured as follows. 
In section \ref{sec:trending} we formalize the concept of trending independently of the application domain and investigate quantification approaches for noise-free and noisy data. 
In particular, we introduce a new graphical method for evaluating trending, the conditional trending plot, which can represent the simultaneous evaluation of different intervals and asymmetries. 
Bootstrap methods for calculating confidence intervals for trending measures are also presented. 
In Section \ref{sec:application}, we show the results of applying our method to several practical examples from measurement, forecasting and nowcasting. 
We conclude our paper with the last section.
The source code for the replication of the results of our study as well as a ready-to-use code for trendability detection are available in our public repository at [Link will be inserted] available.
